### 2020-02-12 ChapterResults/chapterResults.tex
Updated: Late and miss proportion evaluation in Results. Swapped packet-loss graphs around

\subsubsection{Evaluation}
As the speed increases, the mean penetration time increases. With the exception of the starting speed, the standard deviation remains constant below the tolerance line. Once speed increases above the tolerance line, the standard deviation initially increases, but appears to remain constant after the initial increase. Note that the mean error increases in discrete steps (with some small variation), this is due to the discrete physics time-steps. Object speed is application specific and objects need to be travelling directly towards the centre of each other and one of the objects has to be travelling above the tolerance speed, in order for errors to occur.

As latency increases standard deviation remains constant below the tolerance value. With only a small number of exceptions (in $2ms$ experiment), the mean $+2$ standard deviations does not exceed the maximum expected penetration when below the latency tolerance. Above the latency tolerance value, the standard deviation increases for the $16ms$ tolerance experiment, but remains constant for the first two latency experiments. In addition, the first two experiments do not show a clear increase in mean penetration, this is due to the aura calculation's discrete nature and as $15ms$ has been used for the frame-time tolerance, small increases in latency of $2$ and $8ms$ will not show the increase in error to the next discrete step. However, in the final experiment using $16ms$, the relationship of increasing penetration as latency increases is demonstrated.

@@

For the first two frame-time experiments ($8.33ms$ and $15ms$ tolerance values), as frame-time increases, the mean penetration time increases and standard deviation also increases. Standard deviation increases as the delay between frame-time update and physics update can always vary between 0 and the frame-time, meaning even in high frame-time situations, the delay between frame-time update and physics update can be 0. Exceeding the frame-time tolerance very quickly leads to high max error, this is due to the delay in messages being exchanged being created by the long frame-times on both servers (this is reflected in the aura calculation by the frame-time tolerance being multiplied by 2). However, as the target frame-time increases over the tolerance, variation in error increases and max errors become less likely. For the final frame-time experiment, ($33.33ms$ tolerance value), thrashing occurs the majority of the time both above (as demonstrated in \ref{tab_BelowTolerance} and \ref{tab_AboveTolerance}) and below the tolerance, due to this the results shown in \ref{fig_CollisionsPenVsFrameTimeHigh} have a very small sample size and thus will not accurately represent the relationship between frame-time and penetration.

@@

\begin{figure}[t]
	\includegraphics[width=\textwidth]{MeanPenVsLoss}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying packet-loss. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line.}
	%\caption{Penetration time of objects with varying packet-loss. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The number and magnitude of errors increases as packet-loss increases beyond $10\%$.}
	\label{fig_CollisionsPenVsLoss}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLoss}
	\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying packet loss.} %As packet-loss increases from $10\%$ to $20\%$ the ratio of erroneous collisions to correct collisions sharply increases as does misses to total collisions. Above $60\%$ packet-loss, all collisions are missed.}
	\label{fig_RatiosVsLoss}
\end{figure}

>>>>

\subsubsection{Evaluation}
As the speed increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsSpeedLow}, \ref{fig_RatioVsSpeedMid} and \ref{fig_RatioVsSpeedHigh}. When speed is below the speed tolerance, late collisions do not exceed 10\%. This 10\% can be accounted for by false-positives. Once above the speed tolerance, the proportion of late collisions increases immediately, which is predicted by the aura calculation. Missed collisions begin to occur when speed exceed $80ms^{-1}$ in the $48ms^{-1}$ experiment, this is due to objects travelling so quickly, the objects completely pass one another, missing the collision entirely.

It should also be noted that object speed is application specific and objects need to be travelling directly towards the centre of each other and one of the objects has to be travelling above the tolerance speed, in order for errors to occur.

As the speed increases, the mean penetration time increases, as shown in Figs. \ref{fig_CollisionsPenVsSpeedLow}, \ref{fig_CollisionsPenVsSpeedMid} and \ref{fig_CollisionsPenVsSpeedHigh}. With the exception of the starting speed, the standard deviation remains constant below the tolerance line. Once speed increases above the tolerance line, the standard deviation initially increases, but appears to remain constant after the initial increase. Note that the mean error increases in discrete steps (with some small variation), this is due to the discrete physics time-steps.

As the latency increases, the proportion of late collisions to correct collisions increases, as shown in Fig. \ref{fig_RatioVsLatencyHigh}. However, Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyLow} do not show this relationship. In the $2ms$ latency tolerance experiment, late collisions do not exceed $20\%$, which can be accounted for by false-positives. The aura calculation predicts that late collisions should start occurring once $3ms$ has been exceeded, however, this is not observed, as the proportion does not increase above what would be expected for false-positives.
In the $8ms$ latency tolerance experiment, late collisions do not exceed $2\%$, which can be accounted for by false-positives. This remains the case even when the tolerance is exceeded. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached, which this experiment does not reach, therefore no late collisions outside of false-positives are expected. In the $16ms$ latency tolerance experiment, late collisions do not exceed $3\%$ below the tolerance, which can be accounted for by false-positives. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached. In Fig. \ref{fig_RatioVsLatencyHigh} we see the proportion of errors increase from $20ms$ and above, however, it does not exceed the expected false-positive proportion until $25ms$ latency is reached.
%TODO: Re-run latency experiment, larger sample size?

%When latency is below the latency tolerance, late collisions do not exceed 10\%. This 10\% can be accounted for by false-positives. Once above the speed tolerance, the proportion of late collisions increases immediately, which is predicted by the aura calculation.

As latency increases standard deviation remains constant below the tolerance value, as shown in Figs. \ref{fig_CollisionsPenVsLatencyLow}, \ref{fig_CollisionsPenVsLatencyMid} and \ref{fig_CollisionsPenVsLatencyHigh}. With only a small number of exceptions (in $2ms$ experiment), the mean $+2$ standard deviations does not exceed the maximum expected penetration when below the latency tolerance. Above the latency tolerance value, the standard deviation increases for the $16ms$ tolerance experiment, but remains constant for the first two latency experiments. In addition, the first two experiments do not show a clear increase in mean penetration, this is due to the aura calculation's discrete nature and as $15ms$ has been used for the frame-time tolerance, small increases in latency of $2$ and $8ms$ will not show the increase in error to the next discrete step. However, in the final experiment using $16ms$, the relationship of increasing penetration as latency increases is demonstrated.

@@

As frame-time increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyMid}, however in \ref{fig_RatioVsLatencyHigh} the sample size is small above the tolerance line due to the high occurrences of thrashing and so the relationship in this experiment can not be deduced. For the $8ms$ and $15ms$ experiments the late collisions do not exceed 10\% and these can be accounted for by false-positives. In the $8ms$ frame-time tolerance experiment, late collisions are not expected to occur until $16ms$ frame-time, based on the aura size. Late collisions do not exceed $20\%$ and these can all be accounted for by false-positives. In the $15ms$ frame-time tolerance experiment, late collisions exceed $20\%$ once $16ms$ latency is exceeded as predicted by the aura size and increase to over $75\%$ at $30ms$ latency.
In the final frame-time tolerance experiment using $32ms$ frame-time tolerance, late collisions only occur for frame-times of $64ms$. The aura calculation predicts that late collisions should begin to occur as soon as $32ms$ frame-time is exceeded, however, due to the low sample size, as a result of the high occurrences of thrashing, the plot does not accurately represent any relationship between frame-time and proportion of late collisions.

For the first two frame-time experiments ($8.33ms$ and $15ms$ tolerance values), as frame-time increases, the mean penetration time increases and standard deviation also increases, shown in Figs. \ref{fig_CollisionsPenVsFrameLow} and \ref{fig_CollisionsPenVsFrameMid}. Standard deviation increases as the delay between frame-time update and physics update can always vary between 0 and the frame-time, meaning even in high frame-time situations, the delay between frame-time update and physics update can be 0. Exceeding the frame-time tolerance very quickly leads to high max error, this is due to the delay in messages being exchanged being created by the long frame-times on both servers (this is reflected in the aura calculation by the frame-time tolerance being multiplied by 2). However, as the target frame-time increases over the tolerance, variation in error increases and max errors become less likely. For the final frame-time experiment, ($33.33ms$ tolerance value), thrashing occurs the majority of the time both above (as demonstrated in \ref{tab_BelowTolerance} and \ref{tab_AboveTolerance}) and below the tolerance, due to this the results shown in \ref{fig_CollisionsPenVsFrameTimeHigh} have a very small sample size and thus will not accurately represent the relationship between frame-time and penetration.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLoss}
	\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying packet loss.} %As packet-loss increases from $10\%$ to $20\%$ the ratio of erroneous collisions to correct collisions sharply increases as does misses to total collisions. Above $60\%$ packet-loss, all collisions are missed.}
	\label{fig_RatiosVsLoss}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\textwidth]{MeanPenVsLoss}
\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying packet-loss. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line.}
%\caption{Penetration time of objects with varying packet-loss. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The number and magnitude of errors increases as packet-loss increases beyond $10\%$.}
\label{fig_CollisionsPenVsLoss}
\end{figure}
